% !TEX root = paper.tex
% =============================================================
% RAR -- Abstract v0
% Source-of-truth: project_context.md (binding constraints).
% Stage 3 of paper-writing skill. Written LAST per Principle 1.
% Last updated: 2026-07-12
%
% Targets ~200-250 words. Locks:
%   - Headline: forgetting 35.5%--67.5%; mix up to 11.7 pp
%   - Six datasets
%   - Core signal: reconstruction-based old/new compatibility
%   - Design spine (implicit): recon -> routing -> dual heads -> calibration
%
% Conventions:
%   - KDD venue: no \smartparagraph.
%   - Zero hedging, active voice, no em-dashes.
%   - Headline numbers anchored to §4 evaluation.
% =============================================================

\begin{abstract}
Encrypted traffic classification identifies applications and services without inspecting packet payloads, supporting network security, service management, and traffic measurement. Modern representations perform strongly on static, closed-set benchmarks. In practice, however, encrypted-traffic classifiers must continually absorb emerging applications and services without retaining all historical training data. This class-incremental setting is especially challenging because different flows from the same application can exhibit substantial variation, whereas flows from different applications can appear similar due to shared protocols, cloud services, or third-party components. Consequently, compatibility with previously learned class representations varies across flows, yet existing replay and distillation methods typically use fixed global weights and cannot adjust preservation and acquisition accordingly. This limitation calls for a per-flow signal of compatibility with historical traffic patterns. We find that an autoencoder fitted to frozen representations of replayed historical traffic tends to reconstruct old-class flows with lower error than newly arriving flows. Based on this observation, we propose Reconstruction-Aware Routing (RAR), which converts reconstruction error into a continuous per-flow old/new compatibility score. The same score controls both incremental optimization, by weighting preservation and acquisition losses, and inference, by softly combining a frozen historical-class path with a trainable new-class path; logit calibration then supports joint prediction over a unified traffic-class space without task identifiers. Experiments on six public encrypted-traffic datasets show that RAR reduces forgetting by 35.5\%--67.5\% over the evaluated classical CIL baselines and improves mixed-class accuracy by up to 11.7 percentage points. Component, multi-step, and replay-budget studies further support reconstruction-aware old/new balancing.
\end{abstract}
