% !TEX root = paper.tex
% =============================================================
% RAR -- Final Introduction v0
% Source-of-truth: project_context.md (binding constraints).
% Stage 3 of paper-writing skill. Written from scratch per Principle 1.
% Last updated: 2026-07-09
%
% Differs from intro_draft0.tex in:
%   - Key Abstraction now opens with the coined term "knowledge
%     per-flow historical compatibility.
%   - Contributions are claim-first with embedded headline numbers.
%   - Results Preview anchors the closing with the locked headline.
%   - Outline paragraph added at the end.
%
% The Draft 0 introduction (intro_draft0.tex) remains as reference.
% On integration: replace intro_draft0.tex with this file and delete
% the draft. Verify all headline numbers against the final tables.
% =============================================================

\section{Introduction}

% Stakes: problem-first, specific actors. Principle 7: domain before
% method. The ML/AI component enters at the Key Abstraction.
Encrypted-traffic classifiers identify applications and services from packet metadata, length distributions, and timing patterns alone, and the set of classes they must recognize grows continuously. New applications launch, protocol implementations change, and each addition forces the classifier to recognize a class it has never seen. Operators run these classifiers under tight latency budgets and cannot retrain from scratch on every addition; the retraining cost grows with the class history.

% Problem Gap: structural, not quantitative. Three gaps are LOCKED
% in project_context.md and named here to bridge to §3.
Class-incremental learning (CIL) targets this need by adding classes without retraining on the full history. Classical CIL methods use distillation and replay to preserve old knowledge, as in LwF~\cite{li2017lwf}, iCaRL~\cite{rebuffi2017icarl}, and DER~\cite{yan2021der}. Applied to encrypted traffic, three structural gaps remain. First, expanding the classification head makes old and new classes compete for one shared decision boundary. Second, these methods generally balance preservation and acquisition at the dataset or class level rather than adapting the balance to each input. Third, replay depends on a limited buffer that cannot represent the full old-class distribution.

% Key Abstraction: the coined term appears prominently. Per
% rhetorical_moves.md, this move appears ONLY in final versions and is
% framed as compatibility rather than an exclusive assignment claim.
We observe that an autoencoder fitted to frozen features of replayed old samples tends to reconstruct old-class samples with lower error than new-class samples. In encrypted-traffic representations, reconstruction error therefore provides a per-flow score of compatibility with the replay-derived historical-class manifold. Reconstruction-based task gates have used related signals to select task-specific experts~\cite{aljundi2017expertgate}, while OOD-based CIL methods infer a task before applying a corresponding classifier~\cite{kim2022clom,kim2022theoretical,kim2022more,lin2024tpl}. RAR instead uses compatibility as a continuous control signal for balancing old and new traffic classes within one prediction space.

% Design Intuition: one-paragraph mental model. The design spine
% (old/new compatibility -> soft routing -> dual knowledge
% paths -> calibration) is the single line that organizes §3.
RAR (Reconstruction-Aware Routing) is a reconstruction-conditioned CIL framework for encrypted-traffic classification. It turns the compatibility score into a soft routing weight over a frozen old-class path inherited from the preceding step and a trainable path for the arriving classes. The same score weights the distillation and margin objectives, coupling incremental optimization with the inference rule. A logit calibration layer then makes the two class groups comparable in a joint prediction over all seen traffic classes. A reconstruction temperature $\tau$ controls routing softness: small $\tau$ approaches deterministic path selection; large $\tau$ smoothly fuses both paths.

% Contributions: numbered, claim-first. Each item is a claim, not a
% process description. "We show" preferred over "We propose".
We make three contributions.
\begin{enumerate}
  \item \textbf{Reconstruction-conditioned encrypted-traffic CIL.} We formulate compatibility with a replay-derived historical traffic manifold as a continuous per-flow signal for balancing previously learned and newly arriving traffic classes.
  \item \textbf{Calibrated dual-path integration.} We use the same compatibility signal to weight the old-class distillation loss and new-class cross-path margin during training, and to softly route logits between frozen old-class and trainable new-class paths during inference, enabling joint prediction over all seen classes without task identifiers.
  \item \textbf{Evaluation across encrypted-traffic domains.} Across six public datasets, RAR reduces forgetting by 35.5\%--67.5\% and improves mixed-class accuracy by up to 11.7 percentage points over the evaluated classical CIL baselines. Additional studies examine backbone choice, incremental steps, replay budgets, and component contributions.
\end{enumerate}

% Results Preview: anchors the introduction with the locked
% headline numbers. Outlines the rest of the paper so the reader knows
% what each section delivers.
The remainder of this paper evaluates the contribution. \S\ref{sec:background} formalizes the encrypted-traffic CIL problem and its three structural gaps. \S\ref{sec:method} presents RAR's mechanism, from reconstruction error through soft routing to calibration, and closes with a training algorithm (Algorithm~1). \S\ref{sec:eval} reports empirical evidence on six datasets: RAR against classical CIL strategies on ET-BERT, a backbone study confirming that naive forgetting persists across nine encoders, a component ablation, and robustness under multi-step increments and tight replay budgets. \S\ref{sec:related} positions RAR against prior work. \S\ref{sec:conclusion} summarizes the contributions, limitations, and future directions.
